---
title: "hw08"
author: "namanpaul"
date: "November 18, 2015"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Vignette for the package hw08


##Functions created in the class

##`fbind()`

We use this function to bind the factors together

```{r}
library(hw08)
fbind(iris$Species[c(1, 51, 101)], PlantGrowth$group[c(1, 11, 21)])
```

##`freq_out()`

Function used to create a frequency table

```{r}
freq_out(iris$Species)
```

##`m3plot()`

- This function takes in a numeric vector as input, and plots the maximum, mean and minimum values.
- The major inspiration, to create this function for better visualization of the data, as per @jennybc 
- Not very high productive value, but its a quick way to have a glance how the maximum and minimum values look against the mean value on a simple bar plot.

To use this function: 

for example:

we have a numeric vector

```{r}
num_vector <- c(15,20,34,50,60,77,80,89)
m3plot(num_vector)
```

